Hospital Information Technology and Physician Response

### 2022-08-23 Presentations/YESconference.tex
Updates from Overleaf

@@

\begin{frame}{Results: Indicator for Working in Office}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_office_all.pdf}
\end{figure}
$\rightarrow$ 4.6\% increase relative to the mean\\
$\rightarrow$ Driven by young physicians
\end{frame}

@@

\begin{frame}{Results: Indicator for Changing Zip Codes}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_zip_ages.pdf}
\end{figure}
$\rightarrow$ .043 ppt increase in likelihood of retiring for younger physicians (36\%)
$\rightarrow$ This effect is persistent
\end{frame}

@@

\begin{frame}{Summary}
\textcolor{red}{Downside}: evidence that physicians are changing their behavior because of this new technology\\
                \vspace{6mm}
\textcolor{teal}{Potential upside}: For physicians who endure through the implementation of the technology, number of patients goes up and claims per patient goes down

>>>>

\begin{frame}{Physician Response to EHRs}
\centering
\includegraphics[scale=.4]{graphics/EHR tweet.PNG}
\end{frame}

@@

\begin{frame}{Results: Indicator for Working in Office}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_office_all.pdf}
\end{figure}
$\rightarrow$ 4.6\% increase relative to the mean
\end{frame}

\begin{frame}{Results: Indicator for Working in Office (Ages)}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_office_ages.pdf}
\end{figure}
$\rightarrow$ Driven by younger physicians
\end{frame}

@@

\begin{frame}{Results: Indicator for Changing Zip Codes (Ages)}
\begin{figure}[ht]
    \centering
    \includegraphics[scale=.35]{Objects/Presentation_zip_ages.pdf}
\end{figure}
$\rightarrow$ .043 ppt increase in likelihood of retiring for younger physicians (36\%)
$\rightarrow$ This effect is persistent
\end{frame}

@@

\begin{frame}{Summary}
\textcolor{red}{Downside}: evidence that physicians are changing their behavior because of this new technology\\
                \vspace{6mm}
\textcolor{teal}{Potential upside}: For physicians who endure through the implementation of the technology, number of patients goes up and claims per patient goes down\\
                \vspace{6mm}
\underline{Implications}: The way technology is implemented and used is important given the response of the user

### 2022-08-23 Table Code/overall stats.tex
Updates from Overleaf

\caption{Summary Statistics}
\centering
\begin{tabular}[t]{lccccc}
\toprule
Variable & N & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 179,883 & 0.03 & 0.18 & 0 & 1\\
\hspace{1em}Fraction Patients in Office & 179,883 & 0.10 & 0.24 & 0 & 1\\
\hspace{1em}Work in an Office & 179,883 & 0.30 & 0.46 & 0 & 1\\
\hspace{1em}Change Zip Codes & 161,558 & 0.12 & 0.33 & 0 & 1\\
\hspace{1em}Number of Patients & 179,883 & 330 & 274 & 0 & 7,613\\
\hspace{1em}Claim Count & 179,883 & 1,382 & 1,789 & 0 & 64,508\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 179,883 & 0.75 & 0.43 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR & 179,883 & 0.63 & 0.44 & 0 & 1\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 179,883 & 44.9 & 8.4 & 25 & 86\\
\hspace{1em}Female & 179,883 & 0.34 & 0.47 & 0 & 1\\
\hspace{1em}Number of Hospitals Worked With & 179,883 & 1.49 & 0.82 & 1 & 12\\
\hspace{1em}Number of Systems Worked With & 179,883 & 1.31 & 0.60 & 1 & 8\\
\bottomrule
\end{tabular}
\label{tab:sumstats}
\end{table}

>>>>

\caption{Summary Statistics}
\centering
\begin{tabular}[t]{lccccc}
\toprule
Variable & N & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 179,532 & 0.03 & 0.17 & 0 & 1\\
\hspace{1em}Fraction Patients in Office & 179,532 & 0.10 & 0.24 & 0 & 1\\
\hspace{1em}Work in an Office & 179,532 & 0.30 & 0.46 & 0 & 1\\
\hspace{1em}Change Zip Codes & 161,273 & 0.12 & 0.33 & 0 & 1\\
\hspace{1em}Number of Patients & 179,532 & 330.22 & 274.33 & 0 & 7,613\\
\hspace{1em}Claims per Patient & 163,125 & 4.24 & 4.60 & 0 & 679\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 179,532 & 0.75 & 0.43 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR & 179,532 & 0.63 & 0.44 & 0 & 1\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 179,532 & 44.87 & 8.43 & 25 & 86\\
\hspace{1em}Female & 179,532 & 0.34 & 0.47 & 0 & 1\\
\hspace{1em}Number of Hospitals Worked With & 179,532 & 1.49 & 0.82 & 1 & 12\\
\hspace{1em}Number of Systems Worked With & 179,532 & 1.31 & 0.60 & 1 & 8\\
\bottomrule
\end{tabular}
\end{table}
\label{tab:sumstats}
